\begin{center}
	\textbf{ВАРИАНТ 1}
\end{center}

Символом $ \triangleleft $ помечены исправленные ответы на задания.

\subsection*{Task 1}

\begin{enumerate}
	\item 3
	\item 1 $ \triangleleft $
	\item 2
	\item 1
\end{enumerate}

\subsection*{Task 2}

\begin{enumerate}
	\item has been made
	\item is given to
	\item was set up
	\item announced, be deflected $ \triangleleft $
	\item were reported
\end{enumerate}

\subsection*{Task 3}

\begin{enumerate}
	\item Сейчас много внимания уделяется разработке улучшенных методов исследования.
	\item Данное устройство было разработано для создания высокочастотных звуковых волн.
	\item Устройство проходило испытания, когда делегация вошла в лабораторию.
	\item За кратким введением должны последовать вопросы и комментарии.
	\item Когда были получены эти значения, другие методы уже применялись повсеместно.
	\item Движению тела в жидкости или газе препятствует тип трения, называемый вязким трением.
\end{enumerate}

\subsection*{Task 4}

\begin{enumerate}
	\item All complaints should be sent to the head office.
	\item The car works again. Looks like it was repaired. $ \triangleleft $
	\item Jim will probably be sent to England in August. $ \triangleleft $
	\item The room was cleaned when I arrived. $ \triangleleft $
	\item The roof hasn't been repaired yet. $ \triangleleft $
	\item Have you heard the news? Mike was fired. $ \triangleleft $
	\item I don't like being told what to do. $ \triangleleft $
	\item This problem can be solved.
	\item The service is included in the bill.
	\item Was all the money stolen? $ \triangleleft $
\end{enumerate}

